From Water Dynamics to Rainfed Landscapes with GRASS GIS\bigskip

### 2014-04-17 grassposter/2014_EGU_WD_Landscape/poster.tex
update credits
git-svn-id: https://svn.osgeo.org/grass/grass-promo@59761 15284696-431f-4ddb-bdfa-cd5b030d7da7

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\blocknode{Acknowledgements}{
\smallskip
The authors would like to acknowledge the CGIAR Research Program on Water, Land and Ecosystems (WLE ; \url{wle.cgiar.org}) Innovation Fund.\newline
}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\blocknode{Acknowledgements}{
\smallskip
\begin{tabular}{p{0.70\textwidth} c}
	The authors would like to acknowledge the CGIAR Research Program on Water, Land and Ecosystems (WLE ; \url{wle.cgiar.org}) Innovation Fund.
	&
	\hspace{3mm}
	\raisebox{-0.5\totalheight}{\includegraphics[width=0.27\textwidth]{./images/WLE}}
\end{tabular}
}
